---
title: "Assignment 1 ST464"
author: "Ciarán Ó hAoláin"
date: "`r format(Sys.time(), '%X %d %B, %Y')`"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.height = 6 , fig.width = 10)
```


```{r, eval=T, echo=FALSE}
suppressMessages(library(tidyverse))
suppressMessages(library(ggplot2))
suppressMessages(library(GGally))

```



#### Question 4



```{r eval=T} 
w <- read.csv("./worldhappiness2019.csv")
names(w)<- c( "Rank", "Country", "Score", "GDP", "Family",
              "Life", "Freedom", "Generosity", "Trust")
rownames(w)<- w$Country
wscores <- w[,-(1:3)]
```

(a)
```{r}
correlations <- cor(wscores)
correlations
correlations[lower.tri(correlations, diag = TRUE)] = -2
map(1:2, (function(n)
  colnames(correlations)[which.max(apply(correlations, n, max))]))

subset <- wscores[c("GDP", "Life")]
plot(subset)

rownames(subset)[which.min(unlist(subset["Life"]))]

```

The pair of variables with the highest correlation are GDP per capita and healthy life expectancy.

The outlying country on this graph is Swaziland.


(b)
```{r}
dm <- as.matrix(dist(wscores, method = "euclidean"))
d <- dist(wscores, method = "euclidean")
h <- hclust(d, "average")
d1 <- as.dendrogram(h)
suppressMessages(library(dendextend))
d2 <- color_branches(d1, k = 4, col = c(2, 3, 5, 4))
par(cex=0.5)
plot(d2)
```

There is an extreme outlier country, the Central African Republic, while Morocco, Georgia, Albania and Iran are also outliers to a smaller extent.


(c)
```{r}
source("./h1code.R")
clust3 <- cutree(h, 3)
table(clust3)
clust3[c("Ireland", "India")]
partition <- sumPartition(wscores, clust3)
which.max(partition$centroids["Family", ])
```

The cluster sizes are 111, 44 and 1 (let's call these clusters 1, 2 and 3 respectively).
Ireland belongs to cluster 1.
India belongs to cluster 2.
Cluster 1 has the highest Family score.
Cluster 1 has the highest scores overall.


(d)
```{r}
wscoresPartitioned1 <- wscores
wscoresPartitioned1$Cluster <- as.factor(clust3)
ggparcoord(
  wscoresPartitioned1,
  columns = 1:6,
  groupColumn = "Cluster",
  scale = "uniminmax"
) + xlab("Scoring Category") + ylab("Score")
```

The lowest scoring cluster is unusual becuase it has a rather high Freedom and Genoristy value despite otherwise being quite different in value to other clusters on the plot.

(e)
```{r}
set.seed(123)
km <- kmeans(wscores, nstart = 10, centers = 3)
sumPartition(wscores, km$cluster)
```

The outlier countries here are the Central African Republic, Myanmar and Indonesia.


(f)
```{r}
wscoresPartitioned2 <- wscores
wscoresPartitioned2$Cluster <- as.factor(km$cluster)
ggparcoord(wscoresPartitioned2,
           groupColumn = "Cluster",
           scale = "uniminmax",
           columns = 1:6)
```

Cluster 1 has the highest Family score.
Cluster 1 has the highest scores overall.


(g)
```{r}
w$Cluster <- as.factor(km$cluster)
ggplot(w, aes(x = Cluster, y = Score)) + geom_boxplot()
```

The scores are clearly quite well clustered and quite distinct, with little overlap between the different clusters. This show we've effectively clustered the data.